The `zoon` R package for reproducible and shareable species distribution modelling

### 2016-03-21 ms.Rmd
sorting out figure placement ad todying a couple od references

---
title: "The `zoon` R package for reproducible and shareable species distribution modelling"
author: "Nick Golding, Tom August, Tim C.D. Lucas, Emiel Van Loon & Greg McInerny"
date: "21 March 2016"
bibliography: zoon_app.bib
csl: mee.csl
output: 
  pdf_document:
    fig_caption: yes
---

@@

Next, we update the workflow to produce an interactive map enabling anyone to inspect the data and  predictions on a zoomable map, and to inspect the response curves of the fitted model:

@@

![The interactive map module overlay the raw data and predicted distribution, allowing users to interactively explore their results.](./figs/interactive_map.png)

>>>>

---
title: "The `zoon` R package for reproducible and shareable species distribution modelling"
author: "Nick Golding, Tom August, Tim C.D. Lucas, Emiel Van Loon & Greg McInerny"
date: "21 March 2016"
bibliography: zoon_app.bib
csl: mee.csl
output: 
  pdf_document:
    fig_caption: yes
    includes:  
      in_header: latex_preamble.tex
---

@@

Next, we update the workflow to produce an interactive map enabling anyone to inspect the data and  predictions on a zoomable map, and to inspect the response curves of the fitted model. These outputs are shown in Figure \ref{fig:interactive}.

@@

![The interactive map module overlay the raw data and predicted distribution, allowing users to interactively explore their results.\label{fig:interactive}](./figs/interactive_map.png)
